\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2014-04-28 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
updated all the copyright header files

\noindent \begin{centering}
\includegraphics[width=0.119\textwidth]{figures/logo_INGV}\vspace*{2truemm}
\includegraphics[width=0.119\textwidth]{figures/logo_University_of_Toronto}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_Univ_Toulouse}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_TOTAL}\vspace*{2truemm}
\includegraphics[width=0.130\textwidth]{figures/logo_Fairbanks}
\par\end{centering}
\end{figure}

@@

It has very good accuracy and convergence properties \citep{MaPa89,SePr94,DeFiMu02,Coh02,DeSe07,SeOl08,AiWa09,AiWa10,MeStTh12}.
The spectral element approach admits spectral rates of convergence
and allows exploiting $hp$-convergence schemes. It is also very well
suited to parallel implementation on very large supercomputers \citep{KoTsChTr03,TsKoChTr03,KoLaMi08a,CaKoLaTiMiLeSnTr08,KoViCh10}
as well as on clusters of GPU accelerating graphics cards \citep{KoMiEr09,KoErGoMi10,Kom11}.
Tensor products inside each element can be optimized to reach very
high efficiency \citep{DeFiMu02}, and mesh point and element numbering
can be optimized to reduce processor cache misses and improve cache
reuse \citep{KoLaMi08a}. The SEM can also handle triangular (in 2D)
or tetrahedral (in 3D) elements \citep{WinBoyd96,TaWi00,KoMaTrTaWi01,Coh02,MeViSa06}
as well as mixed meshes, although with increased cost and reduced
accuracy in these elements, as in the discontinuous Galerkin method.\\

@@

This new release of the code (version 2.1) includes Convolution or
Auxiliary Differential Equation Perfectly Matched absorbing Layers
(C-PML or ADE-PML) \citep{MaKoEz08,MaKoGe08,MaKo09,MaKoGeBr10,KoMa07}.
It also includes support for GPU graphics card acceleration \citep{KoMiEr09,KoErGoMi10,MiKo10,Kom11}.\\

@@

If you use SPECFEM3D Cartesian for your own research, please cite
at least one of the following articles:
\begin{description}
\item [{Numerical simulations in general}] ~\\
 Forward and adjoint simulations are described in detail in \citet{TrKoLi08,PeKoLuMaLeCaLeMaLiBlNiBaTr11,VaCaSaKoVi99,KoMiEr09,KoErGoMi10,ChKoViCaVaFe07,MaKoDi09,KoViCh10,CaKoLaTiMiLeSnTr08,TrKoHjLiZhPeBoMcFrTrHu10,KoRiTr02,KoTr02a,KoTr02b,KoTr99}
or \citet{KoVi98}. Additional aspects of adjoint simulations are
described in \citet{TrTaLi05,LiTr06,TrKoLi08,LiTr08,TrKoHjLiZhPeBoMcFrTrHu10,PeKoLuMaLeCaLeMaLiBlNiBaTr11}.
Domain decomposition is explained in detail in \citet{MaKoBlLe08},
and excellent scaling up to 150,000 processor cores is shown for instance
in \citet{CaKoLaTiMiLeSnTr08,KoLaMi08a,MaKoBlLe08,KoErGoMi10,Kom11},
\item [{GPU computing}] ~\\
 Computing on GPU graphics cards for acoustic or seismic wave propagation
applications is described in detail in \citet{KoMiEr09,KoErGoMi10,MiKo10,Kom11}.
\end{description}
\noindent If you use this new version 2.1, which has non blocking
MPI for much better performance for medium or large runs, please cite
at least one of these six articles, in which results of non blocking
MPI runs are presented: \citet{PeKoLuMaLeCaLeMaLiBlNiBaTr11,KoErGoMi10,KoViCh10,Kom11,CaKoLaTiMiLeSnTr08,MaKoBlLe08}.\\

@@

The SPECFEM3D Cartesian software package comes in a gzipped tar ball.
In the directory in which you want to install the package, type
\begin{lyxcode}
{\small tar~-zxvf~SPECFEM3D\_V2.1.0\_Cartesian.tar.gz}{\small \par}
\end{lyxcode}
The directory \texttt{\small SPECFEM3D/}{\small{} will then contain
the source code.}\\
{\small \par}

@@

To report bugs or suggest improvements to the code, please send an
e-mail to the CIG Computational Seismology Mailing List \urlwithparentheses{cig-seismo@geodynamics.org}
or Jeroen Tromp \urlwithparentheses{jtromp-AT-princeton.edu}, and/or
use our online bug tracking system Roundup \urlwithparentheses{www.geodynamics.org/roundup}.

@@

Please e-mail your feedback, questions, comments, and suggestions
to Jeroen Tromp \urlwithparentheses{jtromp-AT-princeton.edu} or
to the CIG Computational Seismology Mailing List \urlwithparentheses{cig-seismo@geodynamics.org}.

@@

Princeton University, USA, and CNRS / INRIA / University of Pau, France

$\copyright$ Princeton University and CNRS / INRIA / University of
Pau, July 2012

>>>>

\noindent \begin{centering}
\includegraphics[width=0.119\textwidth]{figures/logo_INGV}\vspace*{2truemm}
\includegraphics[width=0.119\textwidth]{figures/logo_University_of_Toronto}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_Univ_Toulouse}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_TOTAL}\vspace*{2truemm}
\includegraphics[width=0.130\textwidth]{figures/logo_Fairbanks}
\hspace*{3mm}\includegraphics[width=0.130\textwidth]{figures/logo_fondation_Del_Duca}
\par\end{centering}
\end{figure}

@@

It has very good accuracy and convergence properties \citep{MaPa89,SePr94,DeFiMu02,Coh02,DeSe07,SeOl08,AiWa09,AiWa10,MeStTh12}.
The spectral element approach admits spectral rates of convergence
and allows exploiting $hp$-convergence schemes. It is also very well
suited to parallel implementation on very large supercomputers \citep{KoTsChTr03,TsKoChTr03,KoLaMi08a,CaKoLaTiMiLeSnTr08,KoViCh10}
as well as on clusters of GPU accelerating graphics cards \citep{Kom11,MiKo10,KoMiEr09,KoErGoMi10}.
Tensor products inside each element can be optimized to reach very
high efficiency \citep{DeFiMu02}, and mesh point and element numbering
can be optimized to reduce processor cache misses and improve cache
reuse \citep{KoLaMi08a}. The SEM can also handle triangular (in 2D)
or tetrahedral (in 3D) elements \citep{WinBoyd96,TaWi00,KoMaTrTaWi01,Coh02,MeViSa06}
as well as mixed meshes, although with increased cost and reduced
accuracy in these elements, as in the discontinuous Galerkin method.\\

@@

It reached the sustained one petaflop performance level for the first time in February 2013
on the Blue Waters Cray supercomputer at the National Center for Supercomputing Applications (NCSA), located at the University of Illinois at Urbana-Champaign (USA).\\

This new release of the code (version 2.1) includes Convolution or
Auxiliary Differential Equation Perfectly Matched absorbing Layers
(C-PML or ADE-PML) \citep{MaKoEz08,MaKoGe08,MaKo09,MaKoGeBr10,KoMa07}.
It also includes support for GPU graphics card acceleration \citep{Kom11,MiKo10,KoMiEr09,KoErGoMi10}.\\

@@

If you use SPECFEM3D Cartesian for your own research, please cite
at least one of the following articles:
\begin{description}
\item [{Numerical simulations in general}] ~\\
 Forward and adjoint simulations are described in detail in \citet{TrKoLi08,PeKoLuMaLeCaLeMaLiBlNiBaTr11,VaCaSaKoVi99,KoMiEr09,KoErGoMi10,ChKoViCaVaFe07,MaKoDi09,KoViCh10,CaKoLaTiMiLeSnTr08,TrKoHjLiZhPeBoMcFrTrHu10,KoRiTr02,KoTr02a,KoTr02b,KoTr99}
or \citet{KoVi98}. Additional aspects of adjoint simulations are
described in \citet{TrTaLi05,LiTr06,TrKoLi08,LiTr08,TrKoHjLiZhPeBoMcFrTrHu10,PeKoLuMaLeCaLeMaLiBlNiBaTr11}.
Domain decomposition is explained in detail in \citet{MaKoBlLe08},
and excellent scaling up to 150,000 processor cores is shown for instance
in \citet{CaKoLaTiMiLeSnTr08,KoLaMi08a,MaKoBlLe08,KoErGoMi10,Kom11},
\item [{GPU computing}] ~\\
 Computing on GPU graphics cards for acoustic or seismic wave propagation
applications is described in detail in \citet{Kom11,MiKo10,KoMiEr09,KoErGoMi10}.
\end{description}
\noindent If you use this new version 2.1, which has non blocking
MPI for much better performance for medium or large runs, please cite
at least one of these six articles, in which results of non blocking
MPI runs are presented: \citet{PeKoLuMaLeCaLeMaLiBlNiBaTr11,KoErGoMi10,KoViCh10,Kom11,CaKoLaTiMiLeSnTr08,MaKoBlLe08}.\\

@@

To download the SPECFEM3D\_Cartesian software package, type this:
\begin{lyxcode}
git clone --recursive --branch devel https://github.com/geodynamics/specfem3d.git
\end{lyxcode}
{\small \par}

@@

To report bugs or suggest improvements to the code, please send an
e-mail to the CIG Computational Seismology Mailing List \urlwithparentheses{cig-seismo@geodynamics.org}.

@@

Please e-mail your feedback, questions, comments, and suggestions
to the CIG Computational Seismology Mailing List \urlwithparentheses{cig-seismo@geodynamics.org}.

@@

Princeton University, USA, and CNRS / University of Marseille, France

$\copyright$ Princeton University and CNRS / University of Marseille, July 2012
